---
title: "Hw 10"
author: "Colin White"
date: "4/14/2021"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```


```{r}
library(forecast)

studioC <- read.table("~/Desktop/1A School/1A Winter 2021/STAT330/HW10/StudioC.csv", sep =",",header = TRUE)
#attach(StudioC)
```
#1
*We want to use past measures of popularity (Google index) to predict future popularity of studio C.
*We will use time series models becasue we beleive that we can leverage temporal (time) autocorelation to make better predictions. 

#2
* There is a strong autocorrelation, and  it seems to have a seasonality
*Multiple regression methods that assume independance are likeluy not appropriate because there is autocorrelaiton. 

```{r}
plot(studioC$Week, studioC$Google_index, type = "o", xlab="Week", ylab="Google Index", cex.lab = 1.4, pch = 19)
abline(v = (1:4)*26 - 14, col = "red", lwd = 1.5, lty = 2)
Acf(studioC$Google_index,lag.max = 30)
```




#3
* Below, we fit all the models
* We use AIC becasue we are using the model for prediction  and AIC is derived with prediciotn as the goal. 
```{r}

Google_ts = ts(studioC$Google_index, frequency = 26)

ar1 = forecast::Arima(studioC$Google_index, order = c(1,0,0))
ma1 = forecast::Arima(studioC$Google_index, order = c(0,0,1))
arima111 = forecast::Arima(studioC$Google_index, order = c (1,1,1))




sarima111 = forecast::Arima(studioC$Google_index, order = c (1,1,1), seasonal = list(order = c (1,1,1), period = 26))

```

* AR(1) AIC = `r ar1$aic`
* MA(1) AIC = `r ma1$aic`
* ARMA(1,1) AIC = `r arima111$aic`
* SARIMA(1,1,1)$\times$(1,1,1)$_{26}$ AIC = `r sarima111$aic


#4

The fit looks good. 

```{r}
plot(studioC$Week, studioC$Google_index, pch = 20)
lines(studioC$Week, sarima111$fitted, col = "red")
legend("topleft", c("data", "Model fit"), col = c("black", "red"), lwd = c(NA, 4), pch = c(20,NA), cex = 1.4)


```


#5

* l - we dont have to worry about linearity becasue we dont have any quantitaitve (or any) covariates. 
* I - Independence - after time series terms are included we assume that $\epsilon_t$ are all independant. This is justified by the ACF plot, even though there are a couple ACF peaks just outside the significance bounds.
* N - Normality - we argue that this looks ok based on the histogram of residuals
* E - Equal variance - we thing that the fitted vs residuals look oh, so I argue that the equal variabce assumption is met. 


Becasue of Seasonal lags, the model isnt fully initialized untill after the first season. 
```{r}
acf(sarima111$residuals[-c(1:26)])



#hist
hist(sarima111$residuals[-c(1:26)] / sd(sarima111$residuals[-c(1:26)]), breaks = 20, freq = FALSE)
curve(dnorm(x), from = -4, to =4, add = TRUE, col = "red", lwd = 2)


#fitted vs r

par(mar = c(4,4,1,1))
plot(c(sarima111$fitted[-(1:26)]),c(sarima111$residuals[-(1:26)]), xlab = "fitted", ylab ="residual", pch = 19)

abline(h = 0, col = "red")
```


#6
```{r}


test.set = studioC$Google_index[76:length(studioC$Google_index)]
train.set = studioC$Google_index[-c(76:length(studioC$Google_index))]


sarima_train = Arima(train.set, order = c(1,1,1), season = list(order = c(1,1,1), period = 26)) 

sarima_test_pred = forecast(sarima_train, h = 26)

plot(sarima_test_pred)
points(studioC$Week, studioC$Google_index)


bias <- mean(sarima_test_pred$mean - test.set)
bias
rpmse <- sqrt(mean((test.set-sarima_test_pred$mean)^2))
rpmse


diff(range(studioC$Google_index))
sd(studioC$Google_index)
```

#7
```{r}
season_five = forecast(sarima111, h = 26)
plot(season_five)
points(studioC$Week, studioC$Google_index)
```
